---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->
<a href="https://doi.org/10.5281/zenodo.19060380"><img src="https://zenodo.org/badge/1183983786.svg" alt="DOI"></a>

```{r, include = FALSE}
  knitr::opts_chunk$set(
    collapse = TRUE,
    comment = "#>",
    fig.path = "man/figures/README-",
    out.width = "100%"
)
```

# `{fp}`

<!-- badges: start -->
[![Lifecycle: experimental](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://lifecycle.r-lib.org/articles/stages.html#experimental)
<!-- badges: end -->

## Installation

You can install the development version of `{fp}` like so:

```{r}
remotes::install_github("raffdoc/fp")
```

## Run

You can launch the application by running:

```{r, eval = FALSE}
fp::run_app()
```

## About

You are reading the doc about version : `r golem::pkg_version()`

This README has been compiled on the

```{r}
Sys.time()
```

Here are the tests results and package coverage:

```{r, error = TRUE}
devtools::check(quiet = TRUE)
```

```{r echo = FALSE}
unloadNamespace("fp")
```

```{r, error = TRUE}
covr::package_coverage()
```

## Changes

The `create_plot` function in `inst/app_code/plot_fp.r` has been refactored for better stability and error handling:

-   **Input Validation:** Now handles `NULL`, empty, or invalid patient IDs gracefully by returning a blank plot with an informative message.
-   **Optimization:** Patient data and metadata are filtered once at the start of the function, reducing redundant filtering operations.
-   **Compatibility:** Updated deprecated `size` arguments to `linewidth` for compatibility with `ggplot2` (3.4.0+).
-   **Safe Calculations:** Added robust date parsing and checks for missing values before adding vertical lines or text annotations.
-   **Testing:** New unit tests added in `tests/testthat/test-plot_fp.R` to ensure consistent behavior across edge cases.
-   **Dependencies:** Added `lubridate` to `Imports` in the `DESCRIPTION` file.

The `get_data.r` script in `inst/app_code/` has been updated to ensure smooth data updates from the web:

- **Non-Interactive Authentication:** Fixed the Google Sheets authentication flow to strictly use the `flightplan.json` service account key. This ensures that data is updated from the web without requiring a manual browser-based login ("access to Google account").
- **Improved Path Detection:** Enhanced the logic for finding the `flightplan.json` file, checking both the installed package paths and local development directories.
- **Robustness:** Added better error handling and logging during the data fetching process from the Google Spreadsheet.
